Automated optimization of a course of actions in a stochastic environment

### 2016-06-10 paper.Rmd
suds
YEYEYEYE

@@

@@

>>>>

We can observe a similarity between the backpropagation mechanism of artificial neural networks. There is an activation and a backprogpagation of the values.

@@

I implemented an adaptative randomness factor. It has the very *ad hoc* form 
$$\epsilon = 50000/log_{10}(S)^6,$$
where $S$ is the size of the data in bytes. I chose this formula so it equals 99% for a data corresponding to 10000 games. The other learner is penalized and has $\epsilon = 100000/log_{10}(S)^6$ so our learner has time to learn how to win.

@@

###5.4 Improvements

Convolutional layer

Detect all illegal moves
